---
title: "Introduction to sjdatar"
output: 
  rmarkdown::html_vignette:
    self-contained: true
vignette: >
  %\VignetteIndexEntry{Introduction to sjdatar}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(sjdatar)
```

The package `sjdatar` was created to share the datasets collected by the students of Supervised Learning course taught at Federal University of São João del-Rei (UFSJ) in the Industrial Engineering undergraduate. These datasets were used by the students to perform activities about regression and classification modeling. Now they can be used for new students and people interested in supervised learning. New datasets collected by the students will be available in new versions of the package.

## Dataset `aluguel2025sjdr`

Dataset containing information on property rentals in São João del Rei for the year 2025, including prices, property features, and location.

```{r}
data(aluguel2025sjdr)
str(aluguel2025sjdr)
```

## Dataset `apartamentos2024mg`

Dataset containing information about apartments available for sale in Minas Gerais, for the year 2024, including sale prices, property characteristics, and location.

```{r}
data(apartamentos2024mg)
str(apartamentos2024mg)
```

## Dataset `biscoitos`

Dataset containing information about cookies and crackers available in the Brazilian market, including product characteristics, nutritional claims, and brand information.

```{r}
data(biscoitos)
str(biscoitos)
```

## Dataset `carros_eletricos`

Dataset containing information about electric cars available in the market, including battery capacity, efficiency, price, range, top speed, and performance.

```{r}
data(carros_eletricos)
str(carros_eletricos)
```

## Dataset `carrosusados2025webmotors`

Dataset containing information about used cars collected from the Webmotors platform in 2025, including model, manufacturer, prices, vehicle characteristics, year, and mileage.

```{r}
data(carrosusados2025webmotors)
str(carrosusados2025webmotors)
```

## Dataset `celularesnovos2025`

Dataset containing information about new cell phones available in 2025, including price, model, and technical specifications.

```{r}
data(celularesnovos2025)
str(celularesnovos2025)
```

## Dataset `celularesusados`

Dataset containing information about used cell phones, including price, technical specifications, condition, and device features.

```{r}
data(celularesusados)
str(celularesusados)
```

## Dataset `computadores`

Dataset containing information about laptop computers available in the Brazilian market, including brand, processor, memory, storage, and price.

```{r}
data(computadores)
str(computadores)
```

## Dataset `feijoes`

Dataset with measurements on distinct beans found in the Brazilian market.

```{r}
data(feijoes)
str(feijoes)
```

## Dataset `folhasfrutas`

Dataset on measurements obtained through image analysis of fruit tree leaves.

```{r}
data(folhasfrutas)
str(folhasfrutas)
```

## Dataset `motos_usadas`

Dataset containing information about used motorcycles available in the Brazilian market, including brand, model, year, mileage, fuel type, engine displacement, state, and price.

```{r}
data(motos_usadas)
str(motos_usadas)
```

## Dataset `motos_usadas2`

Dataset containing information about used motorcycles available in the Brazilian market, including brand, model, year, mileage, engine displacement, fuel type, transmission, color, and price.

```{r}
data(motos_usadas2)
str(motos_usadas2)
```

## Dataset `simdatac1`

Simulated dataset for binary classification with two continuous predictors drawn from a bivariate normal distribution. The binary response variable is defined based on the Mahalanobis distance from the origin, with added noise, generating two overlapping classes suitable for classification modeling tasks.

```{r}
data(simdatac1)
str(simdatac1)
```

## Dataset `simdatac2`

Simulated dataset for binary classification with two continuous predictors drawn from a bivariate normal distribution. The binary response variable is defined based on a quadratic function of the predictors, with added noise, generating two classes separated by a nonlinear boundary.

```{r}
data(simdatac2)
str(simdatac2)
```

## Dataset `soja`

Dataset containing morphological measurements obtained through image analysis of soybean seeds from different cultivars, for classification purposes.

```{r}
data(soja)
str(soja)
```

## Dataset `temperos`

Dataset containing morphological measurements obtained through image analysis of spice and herb leaves from different species, for classification purposes.

```{r}
data(temperos)
str(temperos)
```
